Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-03 ATVA 2025/experiments.tex
update

@@

>>>>

\textcolor{red}{The number of open nodes we considered for the 5 F(ully)C(onnected)NNs depend neither on the image nor on the particular FCNN, only on the depth of the layer, because the runtime depends crucially on this factor. For FCNNs, we use a simple /2 rule between the number of open nodes of layer+1 vs layer (except last layer=14). For other architectures, we set the number of nodes to obtain similar runtime per layer, by testing a couple of neurons per layer, and use it for all images.}

@@

\textcolor{red}{MNIST FCNN networks use the same open numbers sequence for all images, based on layer depth. CIFAR ConvolutionalNN uses another sequence (the same for all images) [AppendixA, Table6 p22].}
